Roster Review 2

### 2019-04-24 rosterReview_02.Rmd
Some trade scenarios and fixes to pulled data

```{r}
rosters_with_adj_projections %>% 
  filter(grepl('2B',display_position)) %>% 
  ggplot(aes(x=team,y=zar,color=team)) +
  geom_point(aes(text=name_full)) +
  coord_flip() -> sb

ggplotly(sb)

rosters_with_adj_projections %>% 
  filter(grepl('3B',display_position)) %>% 
  ggplot(aes(x=team,y=zar,color=team)) +
  geom_point(aes(text=name_full)) +
  coord_flip() -> tb

ggplotly(tb)

rosters_with_adj_projections %>%
  filter(type == 'batter') %>% 
  mutate(third_base = grepl('3B',display_position),
         second_base = grepl('2B',display_position),
         position = case_when(
           third_base & second_base ~ 'Both',
           third_base ~ '3B',
           second_base ~ '2B',
           TRUE ~ "Other")) %>% 
  mutate(team = fct_relevel(team, "Plouffe There It Is!")) %>% 
  ggplot(aes(x=team,y=zar,color=position)) +
  geom_point(aes(text=name_full)) +
  coord_flip() -> both

ggplotly(both)

rosters_with_adj_projections %>% 
  filter(team == 'Free Agent', 
         grepl('2B|3B',display_position)) %>% 
  arrange(zar %>% desc) %>% 
  head(30) %>% 
  View()

```{r}
proj_batter %>% 
  mutate(zar = if_else(type=="batter",
                       z_sum-z_sum_adj$adj[z_sum_adj$type=="batter"],
                       z_sum-z_sum_adj$adj[z_sum_adj$type=="pitcher"])) %>% 
  filter(grepl("Frazier|Voit|Bell|Bradley|Flores",Name)) %>% 
  arrange(zar %>% desc) %>% 
  select(Name, Team, zar, G:z_sum) %>% 
  View()
```

```{r}
players <- get_players() %>% 
  clean_names() %>% 
  mutate(name_full = stri_trans_general(name_full, "latin-ascii"))

View(players)
```
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

>>>>

```{r}
rosters_with_adj_projections %>% 
  filter(grepl("Plouffe|Painting",team)) %>% 
  select(team, manager, name_full, display_position, zar) %>% 
  arrange(zar %>% desc) %>% 
  View()
  # mutate(zar = janitor::round_half_up(zar)) %>% 
  # write_csv("data/tradeReview_20190423.csv")

rosters_with_adj_projections %>% 
  filter(grepl("Plouffe|Painting",team)) %>% 
  ggplot(aes(x=team,y=zar,color=type)) +
  geom_jitter(aes(text=glue("{name_full} - {display_position}", color=type)), width=.2) +
  coord_flip() -> tv

ggplotly(tv)

rosters_with_adj_projections %>% 
  filter(grepl("Plouffe|Dorn",team)) %>% 
  select(team, manager, name_full, display_position, zar) %>% 
  filter(grepl("Devers|Swarzak|deGrom|Rendon|Alex Colom|David Price",name_full)) %>% 
  group_by(team) %>% 
  summarize(zar = sum(zar))

rosters_with_adj_projections %>% 
  filter(grepl("Plouffe|Painting",team)) %>% 
  select(team, manager, name_full, display_position, zar) %>% 
  filter(grepl("Santana|Robertson|deGrom|Devers",name_full)) %>% 
  group_by(team) %>% 
  summarize(zar = sum(zar))
```
